---
title: "Harmonization exposition : smoking"
output:
  html_document:
    css: ~/GitHub/ialsa-2016-groningen/libs/css/sidebar.css
    highlight: kate
    keep_md: yes
    theme: flatly
    toc: yes
---

<!-- These two chunks should be added in the beginning of every .Rmd that you want to source an .R script -->
<!--  The 1st mandatory chunck  -->
<!--  Set the working directory to the repository's base directory -->
```{r, echo=F, message=F} 
#Don't combine this call with any other chunk 
# cat("Working directory: ", getwd()) # check where you are
  library(knitr)
# Rmd is in "./reports/reportA/reportA.Rmd", but now the root is "./"
  knitr::opts_knit$set(root.dir='../../') 
```

<!--  The 2nd mandatory chunck  -->
<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F}
# set options shared by all chunks
opts_chunk$set(
  results='show', 
  message = TRUE,
  comment = NA, 
  tidy = FALSE,
  fig.height = 4, 
  fig.width = 5.5, 
  out.width = "550px",
  fig.path = 'basic-graphs/',     
  dev = "png",
  dpi = 400
  # fig.path = 'figure_pdf/',     
  # dev = "pdf"#,
  # dev.args=list(pdf = list(colormodel = 'cmyk'))
)
echoChunks <- FALSE
options(width=120) #So the output is 50% wider than the default.
# connect to the file with the underlying R script  
read_chunk("./reports/harmonization-smoking/harmonization-smoking.R") 
```

This report lists the candidate variable for DataScheme variables of the construct **smoking**.

<!-- Load 'sourced' R files.  Suppress the output when loading packages. --> 
```{r load-packages, echo=echoChunks, message=FALSE}
```


<!-- Load the sources.  Suppress the output when loading sources. --> 
```{r load-sources, echo=echoChunks, message=FALSE}
```


<!-- Load any Global functions and variables declared in the R file.  Suppress the output. --> 
```{r declare-globals, echo=echoChunks, results='show', message=FALSE}
```

<!-- Declare any global functions specific to a Rmd output.  Suppress the output. --> 
```{r, echo=echoChunks, message=FALSE}
#Put code in here.  It doesn't call a chunk in the codebehind file.
```
# (I) Exposition

> This report is a record of interaction with a data transfer object (dto) produced by `./manipulation/0-ellis-island.R`. 

The next section recaps this script, exposes the architecture of the DTO, and demonstrates the language of interacting with it.   

## (I.A) Ellis Island

> All data are immigrants.

The script `0-ellis-island.R` is the first script in the analytic workflow. It accomplished the following: 

- (1) Reads in raw data files from the candidate studies   
- (2) Extract, combines, and exports their metadata (specifically, variable names and labels, if provided) into `./data/shared/derived/meta-data-live.csv`, which is updated every time Ellis Island script is executed.   
- (3) Augments raw metadata with instructions for renaming and classifying variables. The instructions are provided as manually entered values in `./data/shared/meta-data-map.csv`. They are used by automatic scripts in later harmonization and analysis.  
- (4) Combines unit and metadata into a single DTO to serve as a starting point to all subsequent analyses.   

<!-- Load the datasets.   -->
```{r load-data, echo=T, results='asis', message=FALSE}
```

<!-- Inspect the datasets.   -->
```{r inspect-data, echo=T, results='show', message=FALSE}
```

<!-- Tweak the datasets.   -->
```{r tweak-data, echo=echoChunks, results='show', message=FALSE}
```

<!-- Basic table view.   -->
```{r basic-table, echo=TRUE, results='show', message=FALSE}
```


## (I.B) Target-H

> Everybody wants to be somebody.

We query metadata set to see what variables are present that tap into the construct `smoking`. These variables constitute the candidates for the DataSchema variables of the harmonized variable.  

```{r view-metadata, echo=TRUE, results='show', message=FALSE}
```
After examining the metadata and reviewing  relevant codebooks, the following operationalization of the harmonized variables for `smoking` have been adopted:

#### (1) `smoke_now` :  **Are you a smoker presently?**  
  - `0` - NO - *healthy choice*  
  - `1` - YES - *unhealthy choice     
  
#### (2) `smoked_ever` **Have you ever smoked?**  
  - `0` - NO - *healthy choice*  
  - `1` - YES - *unhealthy choice*  

These two variables will be manufactured by qualitative harmonization in the Development section. 
 
# (II) Development

Finally we produce a dataset containing the DataSchema variables get schema candidates. 
```{r get-schema-candidates, echo=TRUE, results='show', message=FALSE}
```

View all items in `smoking` construct in [`./reports/harmonization-smoking/data-schema-items.R`](./reports/harmonization-smoking/harmonization-smoking-basic-graphs.html)

## (II.A) `smoke_now`

As the starting point for harmonization process, create response profiles for schema variables from each study. 

```{r declare-schema-sets, echo=TRUE}
```  

```{r export-response-profiles, echo=TRUE}
```  
  
####  **Are you a smoker presently?**  
  - `0` - NO - *healthy choice*  
  - `1` - YES - *unhealthy choice   

### ALSA

Item that can generate values value for the harmonized variable `smoke_now`  are:
```{r target-1-alsa-1, echo=TRUE}
```
and have the following counts of possible combination of values :
```{r target-1-alsa-2, echo=TRUE}
```

The algorithm of harmonization is spelled out below: 
```{r target-1-alsa-3, echo=TRUE}
```


### LBSL
```{r target-1-alsa-1, echo=TRUE}
```
### SATSA
### SHARE
### TILDA

## (II.B) `smoked_ever`

> Have you ever smoked?

### ALSA
### LBSL
### SATSA
### SHARE
### TILDA




# (III) Recapitulation

## (III.A) Look back

## (III.B) Was Made Done

> what is your mark on history? 

## (III.C) New beginnings





