---
title: "Best Subset Selection" 
output:
  html_document:
    css: ~/GitHub/ialsa-2016-groningen/libs/css/sidebar.css
    highlight: kate
    keep_md: yes
    theme: flatly
    toc: yes
    toc_depth: 4
---

<!-- These two chunks should be added in the beginning of every .Rmd that you want to source an .R script -->
<!--  The 1st mandatory chunck  -->
<!--  Set the working directory to the repository's base directory -->
```{r, echo=F, message=F} 
#Don't combine this call with any other chunk 
# cat("Working directory: ", getwd()) # check where you are
  library(knitr)
# Rmd is in "./reports/reportA/reportA.Rmd", but now the root is "./"
  knitr::opts_knit$set(root.dir='../../') 
```

<!--  The 2nd mandatory chunck  -->
<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F}
# set options shared by all chunks
opts_chunk$set(
  results='show', 
  message = TRUE,
  comment = NA, 
  tidy = FALSE,
  fig.height = 9, 
  fig.width = 13, 
  out.width = "700px",
  fig.path = 'smoke_now/',     
  dev = "png",
  dpi = 400
  # fig.path = 'figure_pdf/',     
  # dev = "pdf"#,
  # dev.args=list(pdf = list(colormodel = 'cmyk'))
)
echoChunks <- FALSE
options(width=120) #So the output is 50% wider than the default.
# connect to the file with the underlying R script  
read_chunk("./models/best-subset/best-subset.R") 
```

This report explores possible visualization solution for logistic regression modeling.  


<!-- Load 'sourced' R files.  Suppress the output when loading packages. --> 
```{r load-packages, echo=echoChunks, message=FALSE}
```


<!-- Load the sources.  Suppress the output when loading sources. --> 
```{r load-sources, echo=echoChunks, message=FALSE}
```


<!-- Load any Global functions and variables declared in the R file.  Suppress the output. --> 
```{r declare-globals, echo=echoChunks, results='show', message=FALSE}
```

<!-- Declare any global functions specific to a Rmd output.  Suppress the output. --> 
```{r, echo=echoChunks, message=FALSE}
#Put code in here.  It doesn't call a chunk in the codebehind file.
```
> This report is a record of interaction with a data transfer object (dto) produced by `./manipulation/0-ellis-island.R`. 

The next section recaps this script, exposes the architecture of the DTO, and demonstrates the language of interacting with it.   

# Ellis Island

> All data land on Ellis Island.

The script `0-ellis-island.R` is the first script in the analytic workflow. It accomplished the following: 

- (1) Reads in raw data files from the candidate studies   
- (2) Extract, combines, and exports their metadata (specifically, variable names and labels, if provided) into `./data/shared/derived/meta-data-live.csv`, which is updated every time Ellis Island script is executed.   
- (3) Augments raw metadata with instructions for renaming and classifying variables. The instructions are provided as manually entered values in `./data/shared/meta-data-map.csv`. They are used by automatic scripts in later harmonization and analysis.  
- (4) Combines unit and metadata into a single DTO to serve as a starting point to all subsequent analyses.   

<!-- Load the datasets.   -->
```{r load-data, echo=T, results='asis', message=FALSE}
```

<!-- Inspect the datasets.   -->
```{r inspect-data, echo=T, results='show', message=FALSE}
```


# Meta
```{r meta-table, echo=TRUE, results='show', message=FALSE}
```

<!-- Tweak the datasets.   -->
```{r tweak-data, echo=echoChunks, results='show', message=FALSE}
```

<!-- Basic table view.   -->
```{r basic-table, echo=TRUE, results='show', message=FALSE}
```


# Assembly
 The dto containing harmonized operationalizations is queried to assemble analysis-ready dataset.

```{r assemble, echo=TRUE, results='show', message=FALSE}
```


# Declarations

```{r declare-variables, echo=TRUE}
```

# Specification

```{r model-specification, echo=TRUE}
```

```{r define-modeling-functions, echo=FALSE}
```

# Guide to Models

| a | b |  c| d |
|---|---|---|---|
| x | y | z |   |
|   |   |   |   |


# model A

## Pooled 
`study_name` is entered as a factor.  The data are pooled into the same dataset
```{r model-A-global-1, echo=TRUE, eval=TRUE, result = "show"}
```

```{r model-A-global-2, echo=FALSE, eval=TRUE, result = "asis", message=FALSE}
```

#### best 

Find the best subset using the same covariates
```{r model-A-global-3, echo=TRUE, eval=TRUE, result = "show"}
```

```{r model-A-global-4, echo=FALSE, eval=TRUE, result = "asis", message="FALSE"}
```

## Separate 
`study_name` defines clusters for separate estimation. 
```{r model-A-local-1, echo=TRUE, eval=TRUE, result = "show"}
```

```{r model-A-local-2, echo=FALSE, eval=TRUE, results='asis', message="FALSE"}
```



