---
title: "Harmonize: health"
output:
  html_document:
    css: ~/GitHub/ialsa-2016-groningen/libs/css/sidebar.css
    highlight: kate
    keep_md: yes
    theme: flatly
    toc: yes
---

<!-- These two chunks should be added in the beginning of every .Rmd that you want to source an .R script -->
<!--  The 1st mandatory chunck  -->
<!--  Set the working directory to the repository's base directory -->
```{r, echo=F, message=F} 
#Don't combine this call with any other chunk 
# cat("Working directory: ", getwd()) # check where you are
  library(knitr)
# Rmd is in "./reports/reportA/reportA.Rmd", but now the root is "./"
  knitr::opts_knit$set(root.dir='../../') 
```

<!--  The 2nd mandatory chunck  -->
<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F}
# set options shared by all chunks
opts_chunk$set(
  results='show', 
  message = TRUE,
  comment = NA, 
  tidy = FALSE,
  fig.height = 4, 
  fig.width = 5.5, 
  out.width = "550px",
  fig.path = 'figure_rmd/',     
  dev = "png",
  dpi = 400
  # fig.path = 'figure_pdf/',     
  # dev = "pdf"#,
  # dev.args=list(pdf = list(colormodel = 'cmyk'))
)
echoChunks <- FALSE
options(width=120) #So the output is 50% wider than the default.
# connect to the file with the underlying R script  
read_chunk("./reports/harmonize-health/harmonize-health.R") 
```

This report lists the candidate variable for DataScheme variables of the construct **self-reported health**.

<!-- Load 'sourced' R files.  Suppress the output when loading packages. --> 
```{r load-packages, echo=echoChunks, message=FALSE}
```


<!-- Load the sources.  Suppress the output when loading sources. --> 
```{r load-sources, echo=echoChunks, message=FALSE}
```


<!-- Load any Global functions and variables declared in the R file.  Suppress the output. --> 
```{r declare-globals, echo=echoChunks, results='show', message=FALSE}
```

<!-- Declare any global functions specific to a Rmd output.  Suppress the output. --> 
```{r, echo=echoChunks, message=FALSE}
#Put code in here.  It doesn't call a chunk in the codebehind file.
```
# (I) Exposition

> This report is a record of interaction with a data transfer object (dto) produced by `./manipulation/0-ellis-island.R`. 

The next section recaps this script, exposes the architecture of the DTO, and demonstrates the language of interacting with it.   

## (I.A) Ellis Island

> All data land on Ellis Island.

The script `0-ellis-island.R` is the first script in the analytic workflow. It accomplished the following: 

- (1) Reads in raw data files from the candidate studies   
- (2) Extract, combines, and exports their metadata (specifically, variable names and labels, if provided) into `./data/shared/derived/meta-data-live.csv`, which is updated every time Ellis Island script is executed.   
- (3) Augments raw metadata with instructions for renaming and classifying variables. The instructions are provided as manually entered values in `./data/shared/meta-data-map.csv`. They are used by automatic scripts in later harmonization and analysis.  
- (4) Combines unit and metadata into a single DTO to serve as a starting point to all subsequent analyses.   

<!-- Load the datasets.   -->
```{r load-data, echo=T, results='asis', message=FALSE}
```

<!-- Inspect the datasets.   -->
```{r inspect-data, echo=T, results='show', message=FALSE}
```


### Meta
```{r meta-table, echo=TRUE, results='show', message=FALSE}
```

<!-- Tweak the datasets.   -->
```{r tweak-data, echo=echoChunks, results='show', message=FALSE}
```

<!-- Basic table view.   -->
```{r basic-table, echo=TRUE, results='show', message=FALSE}
```


## (I.B) Target-H

> Everybody wants to be somebody.

We query metadata set to retrieve all variables potentially tapping the construct `self-reported health`. These are the candidates to enter the DataSchema and contribute to  computing harmonized variables. 

***NOTE***: what is being retrieved depends on the manually entered values in the column `construct` of the metadata file `./data/shared/meta-data-map.csv`. To specify a different group of variables, edit the  metadata, not the script. 

```{r view-metadata-1, echo=TRUE, results='show', message=FALSE}
```

View [descriptives : health](https://rawgit.com/IALSA/ialsa-2016-groningen-public/master/describe-health.html) for closer examination of each candidate. 

After reviewing descriptives and relevant codebooks, the following operationalization of the harmonized variables for construct `self-reported health` have been adopted:

#### Target : `poor_health`   
  - `0` - `FALSE` - reference group
  - `1` - `TRUE` - risk factor
  
  
These variables will be generated next, in the Development section. 

# (II) Development

The particulare goal of this section is to ensure that the schema to encode the values for the `poor_health` variable is consisten across studies. 

In this section we will define the schema sets for harmonizing `self-reported health` construct (i.e.  specify which variables from which studies will be contributing to computing harmonized variables ). Each of these schema sets will have a particular pattern of possible response values to these variables, which we will export for inspection as `.csv` tables. We then will manually edit these `.csv` tables, populating new columns that will map values of harmonized variables to the specific response pattern of the schema set variables. We then will import harmonization algorithms encoded in `.csv` tables and apply them to compute harmonized variables in the dataset combining raw and harmonized variables for `self-reported health` construct across studies.

## (II.A) 


### (1) Schema sets
Having all potential variables in categorical format we have defined the sets of data schema variables thus: 
```{r II-A-2-schema-sets-1, echo=TRUE}
```  
Each of these schema sets  have a particular pattern of possible response values, for example:

```{r II-A-2-schema-sets-2, echo=TRUE}
```  
We output these tables into self-standing `.csv` files, so we can manually provide the logic of computing harmonized variables.

```{r II-A-2-schema-sets-3, echo=TRUE}
```  

You can examine them in [`./data/meta/response-profiles-live/](https://github.com/IALSA/ialsa-2016-groningen/tree/master/data/meta/response-profiles-live)

## (II.B) `poor_health`

#### Target : `poor_health`   
  - `0` - `FALSE` - reference group
  - `1` - `TRUE` - risk factor

### ALSA

Items that can contribute to generating values for the harmonized variable `poor_health`  are:
```{r II-B-health-alsa-1, echo=TRUE}
```
We encode the harmonization rule by manually editing the values in a corresponding `.csv` file located in  `./data/meta/h-rules/`. Then, we apply the recoding logic it contains and append the newly created, harmonized variable to the initial data set. 
```{r II-B-health-alsa-2, echo=TRUE}
```


### LBSL
Items that can contribute to generating values for the harmonized variable `poor_health`  are:
```{r II-B-health-lbsl-1, echo=TRUE}
```
We encode the harmonization rule by manually editing the values in a corresponding `.csv` file located in  `./data/meta/h-rules/`. Then, we apply the recoding logic it contains and append the newly created, harmonized variable to the initial data set. 
```{r II-B-health-lbsl-2, echo=TRUE}
```


### SATSA

Items that can contribute to generating values for the harmonized variable `poor_health`  are:
```{r II-B-health-satsa-1, echo=TRUE}
```
We encode the harmonization rule by manually editing the values in a corresponding `.csv` file located in  `./data/meta/h-rules/`. Then, we apply the recoding logic it contains and append the newly created, harmonized variable to the initial data set. 
```{r II-B-health-satsa-2, echo=TRUE}
```

### SHARE

Items that can contribute to generating values for the harmonized variable `poor_health`  are:
```{r II-B-health-share-1, echo=TRUE}
```
We encode the harmonization rule by manually editing the values in a corresponding `.csv` file located in  `./data/meta/h-rules/`. Then, we apply the recoding logic it contains and append the newly created, harmonized variable to the initial data set. 
```{r II-B-health-share-2, echo=TRUE}
```


### TILDA

Items that can contribute to generating values for the harmonized variable `poor_health`  are:
```{r II-B-health-tilda-1, echo=TRUE}
```
We encode the harmonization rule by manually editing the values in a corresponding `.csv` file located in  `./data/meta/h-rules/`. Then, we apply the recoding logic it contains and append the newly created, harmonized variable to the initial data set. 
```{r II-B-health-tilda-2, echo=TRUE}
```



# (III) Recapitulation 

At this point the `dto[["unitData"]]` elements (raw data files for each study) have been augmented with the harmonized variable `poor_health`. We retrieve harmonized variables to view frequency counts across studies: 

```{r III-A-assembly, echo=TRUE}
```


Finally, we have added the newly created, harmonized variables to the raw source objects and save the data transfer object.

```{r save-to-disk, echo=TRUE}
```


