---
title: "Harmonization procedures : smoking"
output:
  html_document:
    keep_md: yes
    toc: yes
---

<!-- These two chunks should be added in the beginning of every .Rmd that you want to source an .R script -->
<!--  The 1st mandatory chunck  -->
<!--  Set the working directory to the repository's base directory -->
```{r, echo=F, message=F} 
#Don't combine this call with any other chunk 
# cat("Working directory: ", getwd()) # check where you are
  library(knitr)
# Rmd is in "./reports/reportA/reportA.Rmd", but now the root is "./"
  knitr::opts_knit$set(root.dir='../../') 
```

<!--  The 2nd mandatory chunck  -->
<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F}
# set options shared by all chunks
opts_chunk$set(
  results='show', 
  message = TRUE,
  comment = NA, 
  tidy = FALSE,
  fig.height = 4, 
  fig.width = 5.5, 
  out.width = "550px",
  fig.path = 'figure_rmd/',     
  dev = "png",
  dpi = 400
  # fig.path = 'figure_pdf/',     
  # dev = "pdf"#,
  # dev.args=list(pdf = list(colormodel = 'cmyk'))
)
echoChunks <- FALSE
options(width=120) #So the output is 50% wider than the default.
# connect to the file with the underlying R script  
read_chunk("./sandbox/harmonization-smoking/harmonization-smoking.R") 
```


<!-- Load 'sourced' R files.  Suppress the output when loading packages. --> 
```{r load-packages, echo=echoChunks, message=FALSE}
```


<!-- Load the sources.  Suppress the output when loading sources. --> 
```{r load-sources, echo=echoChunks, message=FALSE}
```


<!-- Load any Global functions and variables declared in the R file.  Suppress the output. --> 
```{r declare-globals, echo=echoChunks, results='show', message=FALSE}
```

<!-- Declare any global functions specific to a Rmd output.  Suppress the output. --> 
```{r, echo=echoChunks, message=FALSE}
#Put code in here.  It doesn't call a chunk in the codebehind file.
```
## General introduction

> This report is meant to be compiled after having executed the script `./manipulation/0-ellis-island.R`, which prepares the necessary data transfer object (DTO). We begin with a brief recap of this script and the DTO it produces.  

## Ellis Island

> All data arrive to Ellis Island. 

The script `0-ellis-island.R` is the first script in the analytic workflow. It accomplished the following: 

- (1) Reads in raw data files from the candidate studies   
- (2) Extract, combines, and exports their metadata (specifically, variable names and labels, if provided) into `./data/shared/derived/meta-data-live.csv`, which is updated every time Ellis Island script is executed.   
- (3) Augments raw metadata with instructions for renaming and classifying variables. The instructions are provided as manually entered values in `./data/shared/meta-data-map.csv`. They are used by automatic scripts in later harmonization and analysis.  
- (4) Combines unit and metadata into a single DTO to serve as a starting point to all subsequent analyses.   

<!-- Load the datasets.   -->
```{r load-data, echo=T, results='show', message=FALSE}
```

<!-- Inspect the datasets.   -->
```{r inspect-data, echo=T, results='show', message=FALSE}
```

<!-- Tweak the datasets.   -->
```{r tweak-data, echo=echoChunks, results='show', message=FALSE}
```

<!-- Basic table view.   -->
```{r basic-table, echo=TRUE, results='show', message=FALSE}
```


## Harmonization potential 

We query metadata set to see what variables are present that tap into the construct `smoking`. These variables constitute the candidates for the DataSchema variables of the harmonized variable.  After examining the metadata and reviewing  relevant codebooks, the following operationalization of the harmonized variables for `smoking` have been adopted:

```{r view-metadata, echo=TRUE, results='show', message=FALSE}
```

### Harmonized Item : **Smoke now** 

* Item `smoke_now` :  *Is respondent a current smoker?*
* Values:     
 - `0` - no (healthy choice)
 - `1` - yes (unhealthy choice)

### Harmonized Item : **Smoked ever**

* Item `smoked_ever` : *Has respondent every smoked?*
* Values:     
 - `0` - no, (healthy choice)
 - `1` - yes, (unhealthy choice)


## DataSchema variables

```{r get-schema-variables, echo=TRUE, results='show', message=FALSE}
```

### ALSA
```{r basic-graphs-alsa, echo=TRUE, results='show', message=FALSE}
```

### LBSL
```{r basic-graphs-lbsl, echo=TRUE, results='show', message=FALSE}
```

### SATSA
```{r basic-graphs-satsa, echo=TRUE, results='show', message=FALSE}
```

### SHARE
```{r basic-graphs-share, echo=TRUE, results='show', message=FALSE}
```

## TILDA
```{r basic-graphs-tilda, echo=TRUE, results='show', message=FALSE}
```




