---
title: "Describe: alcohol"
output:
  html_document:
    css: ~/GitHub/ialsa-2016-groningen/libs/css/sidebar.css
    highlight: kate
    keep_md: yes
    theme: flatly
    toc: yes
---

<!-- These two chunks should be added in the beginning of every .Rmd that you want to source an .R script -->
<!--  The 1st mandatory chunck  -->
<!--  Set the working directory to the repository's base directory -->
```{r, echo=F, message=F} 
#Don't combine this call with any other chunk 
# cat("Working directory: ", getwd()) # check where you are
  library(knitr)
# Rmd is in "./reports/reportA/reportA.Rmd", but now the root is "./"
  knitr::opts_knit$set(root.dir='../../') 
```

<!--  The 2nd mandatory chunck  -->
<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F}
# set options shared by all chunks
opts_chunk$set(
  results='show', 
  message = FALSE,
  comment = NA, 
  tidy = FALSE,
  fig.height = 4, 
  fig.width = 5.5, 
  out.width = "550px",
  fig.path = 'basic-graphs/',     
  dev = "png",
  dpi = 400
  # fig.path = 'figure_pdf/',     
  # dev = "pdf"#,
  # dev.args=list(pdf = list(colormodel = 'cmyk'))
)
echoChunks <- FALSE
options(width=120) #So the output is 50% wider than the default.
# connect to the file with the underlying R script  
read_chunk("./reports/harmonize-alcohol/describe-alcohol.R") 
```

This report lists the candidate variable for DataScheme variables of the construct **alcohol**.

<!-- Load 'sourced' R files.  Suppress the output when loading packages. --> 
```{r load-packages, echo=echoChunks }
```


<!-- Load the sources.  Suppress the output when loading sources. --> 
```{r load-sources, echo=echoChunks }
```


<!-- Load any Global functions and variables declared in the R file.  Suppress the output. --> 
```{r declare-globals, echo=echoChunks }
```

<!-- Declare any global functions specific to a Rmd output.  Suppress the output. --> 
```{r, echo=echoChunks }
#Put code in here.  It doesn't call a chunk in the codebehind file.
```
# Exposition

> This report is meant to be compiled after having executed the script `./manipulation/0-ellis-island.R`, which prepares the necessary data transfer object (DTO). We begin with a brief recap of this script and the DTO it produces.  

## Ellis Island

> All data land on Ellis Island.

The script `0-ellis-island.R` is the first script in the analytic workflow. It accomplished the following: 

- (1) Reads in raw data files from the candidate studies   
- (2) Extract, combines, and exports their metadata (specifically, variable names and labels, if provided) into `./data/shared/derived/meta-data-live.csv`, which is updated every time Ellis Island script is executed.   
- (3) Augments raw metadata with instructions for renaming and classifying variables. The instructions are provided as manually entered values in `./data/shared/meta-data-map.csv`. They are used by automatic scripts in later harmonization and analysis.  
- (4) Combines unit and metadata into a single DTO to serve as a starting point to all subsequent analyses.   

<!-- Load the datasets.   -->
```{r load-data, echo=T}
```

<!-- Inspect the datasets.   -->
```{r inspect-data, echo=T }
```

### Meta
```{r meta-table, echo=TRUE, results='show', message=FALSE}
```


<!-- Tweak the datasets.   -->
```{r tweak-data, echo=echoChunks }
```

<!-- Basic table view.   -->
```{r basic-table, echo=TRUE }
```

# ALSA

## FR6ORMOR
```{r alsa-FR6ORMOR, echo=TRUE }
```

## FREQALCH
```{r alsa-FREQALCH, echo=TRUE }
```

## NOSTDRNK
```{r alsa-NOSTDRNK, echo=TRUE }
```




# LBSL

## ALCOHOL
```{r lbsl-ALCOHOL, echo=TRUE }
```

## BEER
```{r lbsl-BEER, echo=TRUE }
```

## HARDLIQ
```{r lbsl-HARDLIQ, echo=TRUE }
```

## WINE
```{r lbsl-WINE, echo=TRUE }
```



# SATSA

## GALCOHOL
```{r satsa-GALCOHOL, echo=TRUE }
```

## GBEERX
```{r satsa-GBEERX, echo=TRUE }
```

## GBOTVIN
```{r satsa-GBOTVIN, echo=TRUE }
```

## GDRLOTS
```{r satsa-GDRLOTS, echo=TRUE }
```

## GEVRALK
```{r satsa-GEVRALK, echo=TRUE }
```

## GFREQBER
```{r satsa-GFREQBER, echo=TRUE }
```

## GFREQLIQ
```{r satsa-GFREQLIQ, echo=TRUE }
```

## GFREQVIN
```{r satsa-GFREQVIN, echo=TRUE }
```

## GLIQX
```{r satsa-GLIQX, echo=TRUE }
```

## GSTOPALK
```{r satsa-GSTOPALK, echo=TRUE }
```

## GVINX
```{r satsa-GVINX, echo=TRUE }
```




# SHARE

## BR0100
```{r share-BR0100, echo=TRUE }
```

## BR0110
```{r share-BR0110, echo=TRUE }
```

## BR0120
```{r share-BR0120, echo=TRUE }
```

## BR0130
```{r share-BR0130, echo=TRUE }
```



# TILDA

## DRINKSPERDAY
```{r tilda-BEHALC.DRINKSPERDAY, echo=TRUE }
```

## DRINKSPERWEEK
```{r tilda-BEHALC.DRINKSPERWEEK, echo=TRUE }
```

## BEHALC.FREQ.WEEK
```{r tilda-BEHALC.FREQ.WEEK, echo=TRUE }
```

## SCQALCOFREQ
```{r tilda-SCQALCOFREQ, echo=TRUE }
```

## SCQALCOHOL
```{r tilda-SCQALCOHOL, echo=TRUE }
```

## SCQALCONO1
```{r tilda-SCQALCONO1, echo=TRUE }
```

## SCQALCONO2
```{r tilda-SCQALCONO2, echo=TRUE }
```





```{r}
sessionInfo()

```



